Simulations to test ctwas summary stats version, 45k samples, a few new setings required

### 2023-06-18 analysis/simulation-ctwas-ukbWG-gtex.adipose_s80.45_03222023.Rmd
revision figures

simutags <- paste(6, 1:20, sep = "-")
plot_par(1, runtag, simutags)
print("When running with L= 5 in final step:")
plot_PIP(3, runtag, simutags)
print("When running with L= 1 in final step:")
plot_PIP(2, runtag, simutags)

simutags <- paste(7, 1:20, sep = "-")
plot_par(1, runtag, simutags)
print("When running with L= 5 in final step:")
plot_PIP(3, runtag, simutags)
print("When running with L= 1 in final step:")
plot_PIP(2, runtag, simutags)

simutags <- paste(11, 1:20, sep = "-")
plot_par(1, runtag, simutags)
print("When running with L= 5 in final step:")
plot_PIP(3, runtag, simutags)
print("When running with L= 1 in final step:")
plot_PIP(2, runtag, simutags)

simutags <- paste(8, c(1:13,15:20), sep = "-")
plot_par(1, runtag, simutags)
print("When running with L= 5 in final step:")
plot_PIP(3, runtag, simutags)
print("When running with L= 1 in final step:")
plot_PIP(2, runtag, simutags)

simutags <- paste(9, 1:20, sep = "-")
plot_par(1, runtag, simutags)
print("When running with L= 5 in final step:")
plot_PIP(3, runtag, simutags)
print("When running with L= 1 in final step:")
plot_PIP(2, runtag, simutags)
```

>>>>

simutags <- paste(6, 1:20, sep = "-")
plot_par(1, runtag, simutags)
print("When running with L= 5 in final step:")
plot_PIP(1, runtag, simutags)
print("When running with L= 1 in final step:")
plot_PIP(2, runtag, simutags)

simutags <- paste(7, 1:20, sep = "-")
plot_par(1, runtag, simutags)
print("When running with L= 5 in final step:")
plot_PIP(1, runtag, simutags)
print("When running with L= 1 in final step:")
plot_PIP(2, runtag, simutags)

simutags <- paste(11, 1:20, sep = "-")
plot_par(1, runtag, simutags)
print("When running with L= 5 in final step:")
plot_PIP(1, runtag, simutags)
print("When running with L= 1 in final step:")
plot_PIP(2, runtag, simutags)

simutags <- paste(8, c(1:20), sep = "-")
plot_par(1, runtag, simutags)
print("When running with L= 5 in final step:")
plot_PIP(1, runtag, simutags)
print("When running with L= 1 in final step:")
plot_PIP(2, runtag, simutags)

simutags <- paste(9, 1:20, sep = "-")
plot_par(1, runtag, simutags)
print("When running with L= 5 in final step:")
plot_PIP(1, runtag, simutags)
print("When running with L= 1 in final step:")
plot_PIP(2, runtag, simutags)
```
